Hydras, Ordinals \& Co.\\ A library in Coq of entertaining formal mathematics

### 2021-10-22 doc/chapter-powers.tex
fix typos
add a link to Yves' file fib.v

In~\cite{BC04}, several exercises~\footnote{Exercises 9.8 (page 270), 9.10 (page 271), 9.15 (page 276), 9.17 (page 284), and 15.8 (page 418).}
present ways to compute Fibonacci numbers, with the less number of recursive calls  as possible. Please note that these optimizations and the formal proof of their correctness are \emph{ad-hoc}, \emph{i.e.}, exclusively written for the
Fibonacci numbers.
In contrast, the optimizations we present in this document apply, in their vast majority, \emph{generic} techniques of efficient computation of powers in a monoid. 
This example of Fibonacci numbers has been developed with Yves Bertot, who wrote a first version with \texttt{SSreflect/Mathcomp}~\cite{MCB}.

@@

Page.~\pageref{sect:test-strat}, we compare the three strategies with respect to the length of the built chains.

>>>>

In~\cite{BC04}, several exercises~\footnote{Exercises 9.8 (page 270), 9.10 (page 271), 9.15 (page 276), 9.17 (page 284), and 15.8 (page 418).}
present ways to compute Fibonacci numbers, with the less number of recursive calls  as possible. Please note that these optimizations and the formal proof of their correctness are \emph{ad-hoc}, \emph{i.e.}, exclusively written for the
Fibonacci numbers.
In contrast, the optimizations we present in this document apply, in their vast majority, \emph{generic} techniques of efficient computation of powers in a monoid. 
This example of Fibonacci numbers has been developed with Yves Bertot, who wrote a first version with \texttt{SSreflect/Mathcomp}~\cite{MCB}. This original version is available on
\href{../theories/html/additions.fib.html}{additions.fib}.

@@

Page~\pageref{sect:test-strat}, we compare the three strategies with respect to the length of the built chains.
